Microclimatic spatial variation buffers local warming in alpine vegetation

### 2022-02-15 doc/manuscript.Rmd
minor changes ms

---
title: "Microclimatic spatial variation buffers local warming in alpine vegetation"
output: github_document
bibliography: refs.bib
csl: annals-of-botany.csl
link-citations: yes
always_allow_html: true
---

@@

>>>>

---
title: "Microclimatic spatial variation buffers local warming in alpine vegetation"
output: html_document
bibliography: refs.bib
csl: annals-of-botany.csl
link-citations: yes
always_allow_html: true
---

@@

## Figures

```{r fig1, echo = FALSE, fig.pos = "H", fig.cap = "**Figure 1** Study system."}
knitr::include_graphics("../results/figures/survey-sites.png")
```

```{r fig2, echo = FALSE, fig.pos = "H", fig.cap = "**Figure 1** Study system."}
knitr::include_graphics("../results/figures/temperature-logs.png")
```

```{r fig3, echo = FALSE, fig.pos = "H", fig.cap = "**Figure 1** Study system."}
knitr::include_graphics("../results/figures/pca-temperatures.png")
```

```{r fig4, echo = FALSE, fig.pos = "H", fig.cap = "**Figure 1** Study system."}
knitr::include_graphics("../results/figures/nmds-species.png")
```

```{r fig5, echo = FALSE, fig.pos = "H", fig.cap = "**Figure 1** Study system."}
knitr::include_graphics("../results/figures/spp-changes.png")
```
